A Generalized Sphere Theorem for Positively Curved Combinatorial 3-Manifolds

### 2013-06-10 paper/paper.tex
more writing.

A small Python program was created to examine each manifold in the census and compute its diameter. See Figure \ref{fig:global_statistics} for a plot of the number of manifolds by topological type and diameter. Note that, as claimed, every manifold with diameter greater than $J$ is a 3-sphere. The corresponding data using the coarser-grained edge-diameter can be found in Figure \ref{fig:global_statistics_edges}.

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.6\linewidth]{figures/global_statistics.png}
    \caption{Global statistics. TO DO: CHANGE DIAMETER LABELS TO $1, H, 2, J, 3, 2H, 4, 2J$ AND PUT THESE ON HORIZONTAL AXIS. TO DO: CHANGE GRAPH TO SHOW SEPARATE DATA POINTS FOR EACH TOPOLOGICAL TYPE. TO DO: CREATE ANOTHER GRAPH WITH JUST EDGE DIAMETER COUNTS}
    \end{center}
    \label{fig:global_statistics}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=0.6\linewidth]{figures/global_statistics.png}
    \caption{...TO DO}
    \end{center}
    \label{fig:global_statistics_edges}
\end{figure}

@@

\section{Discussion}

TO DO: BIG PICTURE STUFF ABOUT EXTENDIND EDGE PATHS. WHY DOES IT HELP? CAN WE USE IT TO DO OTHER NICE THINGS? INCORPORATE FOLLOWING STUFF INTO DISCUSSION ...

>>>>

A small Python program was created to examine each manifold in the census and compute its diameter. See Figure \ref{fig:global_statistics} for a plot of the number of manifolds by topological type and diameter. As claimed, every manifold with diameter greater than $J$ is a 3-sphere. The corresponding data using the coarser-grained edge-diameter can be found in Figure \ref{fig:global_statistics_edges}. Note that there are $3$-manifolds homeomor

\begin{figure}
    \begin{center}
    \includegraphics[width=0.6\linewidth]{figures/global_statistics.png}
    \caption{Global statistics. TO DO: CHANGE DIAMETER LABELS TO $1, H, 2, J, 3, 2H, 4, 2J$ AND PUT THESE ON HORIZONTAL AXIS. TO DO: CHANGE GRAPH TO SHOW SEPARATE DATA POINTS FOR EACH TOPOLOGICAL TYPE. TO DO: CREATE ANOTHER GRAPH WITH JUST EDGE DIAMETER COUNTS}
    \end{center}
    \caption{TO DO: ADD CAPTION}
    \label{fig:global_statistics}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=0.6\linewidth]{figures/global_statistics.png}
    \end{center}
    \caption{TO DO: ADD CAPTION}
    \label{fig:global_statistics_edges}
\end{figure}

@@

@@

\section{Discussion}
Why does adding additional paths above and beyond edge-paths restore the classical structure to our proof?
